Estimating duration in the presence of misclassification

### 2023-09-12 cis-imperfect-testing.tex
Notes on what should go in imperfect testing chapter

@@

>>>>

\begin{itemize}
  \item When sensitivity is too bad (0.6), cannot recover the true distribution. The assumptions in the model, that the first test is a true positive and no missed infections prior, cannot hold.
  \item Assuming too low a test sensitivity (bottom left triangle) means that number of missed infections will be overestimated and the duration distribution will be overestimated (\ie episodes are too long on average).
\end{itemize}

@@

\begin{itemize}
  \item Survival prior matters for quantitative details but not qualitative shape. 
  \item Number of missed infections prior is more important.
  \item Unclear why this is the case, probably model misspecification meaning that fewer missed infections than expected.
  \item Two possible misspecifications: test sensitivity (not constant) and constant incidence.
\end{itemize}
